Hierarchy Builder

### 2020-06-19 coqws/easychair.tex
small fix
being a bit more verbose about CMonoid

In this talk we focus on how to use \HB{} in a Coq development without
any prior knowledge, walking slowly through the example below,
describing the bricks of the language from mixins -- i.e. bare bone building
block of the hierarchy, it packs operations and axioms -- to structures.

@@

We first introduce the base structure of our example,
\verb-CMonoid-, which is defined in two phases: first its contents
using \verb-HB.mixin- and then the structure itself is declared using
\verb-HB.structure.-

>>>>

In this talk we focus on how to use \HB{} in a Coq development without
any prior knowledge, walking slowly through the example below,
describing the bricks of the language from mixins -- i.e. bare bone building
block of the hierarchy, packing operations and axioms -- to structures.

@@

We first introduce the base structure of our example, the structure
\verb-CMonoid- of commutative monoids, which is defined in two phases:
first its contents using \verb-HB.mixin- and then the structure itself
is declared using \verb-HB.structure.-
